### 2023-02-13 article.tex
Remove recommendations to supmat
Fix table

\begin{table}[h]
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Term         & Definition                                                                   & Example                                                         \\
    \hline
    Code         & Body of text to be run by a computer                                         & The scripts run by a computational experiment                   \\
    Data         & Individual facts, statistics, or items of information                        & The name of a SNP known to have a significant association       \\
    Genotype     & The DNA allele at a certain location                                         & AA, AC, CG, GT, ...                                             \\
    Paradata     & Data that describe the process of generating data                            & The code to conclude that a SNP has a significant association   \\
    Phenotype    & How an organism looks like in the broadest sense                             & The concentration of IL6RA in the blood                         \\
    Primary data & Data that is the foundation of an experiment                                 & The genotype of individuals                                     \\
    Metadata     & Data that provide information about other data                               & The article that describes an experiment                        \\
    Raw data     & Data directly from the real world, that are not yet ready to be primary data & The raw results of getting the genotypes of individuals         \\
    SNP          & A named location within a genome                                             & \verb|rs12133641|                                               \\
    Trait        & A phenotype                                                                  & The concentration of IL6RA in the blood                         
    \hline
  \end{tabular}
  \caption{Terms used in this paper, and their definitions}
  \label{tab:definitions}
\end{table}

>>>>

\begin{table}[h]
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Term         & Definition                                                                   & Example                                                         \\
    \hline
    Code         & Body of text to be run by a computer                                         & The scripts run by a computational experiment                   \\
    Data         & Individual facts, statistics, or items of information                        & The name of a SNP known to have a significant association       \\
    Genotype     & The DNA allele at a certain location                                         & AA, AC, CG, GT, ...                                             \\
    Paradata     & Data that describe the process of generating data                            & The code to conclude that a SNP has a significant association   \\
    Phenotype    & How an organism looks like in the broadest sense                             & The concentration of IL6RA in the blood                         \\
    Primary data & Data that is the foundation of an experiment                                 & The genotype of individuals                                     \\
    Metadata     & Data that provide information about other data                               & The article that describes an experiment                        \\
    Raw data     & Data directly from the real world, that are not yet ready to be primary data & The raw results of getting the genotypes of individuals         \\
    SNP          & A named location within a genome                                             & \verb|rs12133641|                                               \\
    Trait        & A phenotype                                                                  & The concentration of IL6RA in the blood                         \\
    \hline
  \end{tabular}
  \caption{Terms used in this paper, and their definitions}
  \label{tab:definitions}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Recommendations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
